\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking} % Style options: casual, classic, banking, oldstyle, fancy
\moderncvcolor{blue}  % Color options: blue, orange, green, red, purple, grey
\usepackage[scale=0.9]{geometry}  % Adjust page margins

% Personal data
\name{Eric}{Allatta}
\phone[mobile]{929-244-0482}
\email{ericallatta@gmail.org}
\social[linkedin]{linkedin.com/in/ericallatta} % Update with actual LinkedIn profile if available

\begin{document}

\makecvtitle
\vspace*{-2\baselineskip}

% Summary
\section{Summary}
Experienced mathematics and computer science educator with over a decade in NYC public schools. Passionate about integrating computing into math education to build students' problem-solving skills. Committed to fostering an inclusive, collaborative, and reflective classroom where students develop fluency in computational and mathematical thinking. Skilled in curriculum design, data management, and teacher training.

% Certifications
\section{Certifications}
\cventry{}{New York State 7-12 Mathematics Professional Certification}{}{}{}{}
\cventry{}{Pursuing New York State K-12 Computer Science Certification}{}{}{}{}

% Experience
\section{Experience}
\cventry{2012--2021}{Mathematics \& Computer Science Teacher}{NYCDOE, Academy for Software Engineering}{New York, NY}{}{
  \begin{itemize}
    \item Designed and implemented integrated mathematics and computer science curricula, leading to increased student engagement and improved computational thinking skills in Algebra and AP CS Principles students.
    \item Developed school-wide data systems that streamlined student performance tracking, improving instructional decision-making and intervention strategies.
    \item Piloted and evaluated cutting-edge computing curricula in diverse high school classrooms.
  \end{itemize}
}

\cventry{2014--Present}{Lead Master Teacher}{Bootstrap}{New York, NY}{}{
  \begin{itemize}
    \item Trained multiple cohorts of teachers in integrated computing curricula for Algebra, Data Science, and Physics.
    \item Provided curriculum development feedback, pilot testing, and live coaching for educators.
  \end{itemize}
}

\cventry{2013--2021}{Pilot Teacher \\ \& Consultant}{CollegeBoard}{New York, NY}{}{
  \begin{itemize}
    \item Designed and implemented curriculum aligned with the AP CS Principles framework.
    \item Led CS Principles training sessions for AP Summer Institutes.
  \end{itemize}
}

\cventry{2012--2021}{Master Teacher Fellow}{Math for America}{New York, NY}{}{
  \begin{itemize}
    \item Designed and led computing and data science workshops for NYC educators.
  \end{itemize}
}

\cventry{2021--Present}{Data Management Consultant}{Self-Employed}{Santa Fe, NM}{}{
  \begin{itemize}
    \item Developed automated data management systems for small businesses in agriculture, education, and woodworking industries.
  \end{itemize}
}

% Education
\section{Education}
\cventry{2011--2012}{Master’s in Urban Adolescent Mathematics Education}{Hunter College, City University of New York}{New York, NY}{}{}
\cventry{2003--2007}{Bachelor of Arts in the Liberal Arts}{St. John’s College}{Santa Fe, NM}{}{}

\end{document}
